Figures to insert in text

### 2018-04-09 Chapters/Chapter02.tex
sociology of science comment

This time, however, it will be running on a computer:  implicit assumptions will emerge; anomalies between expected theory and numerical results will appear; and reproducible experiments will be conducted.

@@

Let us revisit, in these concluding thoughts, the emphasis employed over speed of computation.  At first sight, that might seem like a typical objective of efficiency in computer science. But we are not only interested in the computer science effects here --- the ambition is different. More important than this `computer-sciency' goal, i.e., a beautiful, clean, efficient algorithm with the primary effect of enhanced speed, however, is the secondary effect on the sociology of science:  \emph{We can see farther}.

Beyond speed, I have also strived for \emph{ease of use}.  All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. I have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. We invite the reader to take a look and explore a little bit.

>>>>

This time, however, it will be running on a computer:   anomalies between expected theory and numerical results will appear; implicit, hidden, assumptions will emerge; and reproducible experiments will be conducted.

@@

Let us revisit, in these concluding thoughts, the emphasis employed over speed of computation.  At first sight, that might seem like a typical objective of efficiency in computer science. But we are not only interested in the computer science effects here --- the ambition is different. More important than this `computer-sciency' goal, i.e., a beautiful, clean, efficient algorithm with the primary effect of enhanced speed, however, is the secondary effect on the sociology of science:  communities form around open-source code, specialists in a particular arena magnify the capabilities of the code, debates and meetings are regularly held, and deep divisive disagreements lead to community splits in multiple potential directions of exploration.  In a very real sense, given a shared code to work and experiment on, we can see farther.

Beyond speed, I have also strived for \emph{ease of use} and \emph{replicable studies}.  All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. Most importantly, they also serve as a tutorial for learning about the framework's design, and perhaps as a teaching tool for SDM itself. I have generated a Docker image, which makes it even easier to explore the framework by delegating heavy computational work to cloud services. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. We invite the reader to take a look and explore a little bit.
